### 2013-02-15 mcmc.tex
outline notes
outline points

...Some guidance of where this comes back up below..

@@

...You can't sample the likelihood!  You can only sample a posterior
pdf!
% *********** BJB
% YES!!!! Although you can sample the likelihood if your samples are in
% data space. :)

>>>>

...Is there any way to reconstruct $p(x)$ from the samples
$\setofall{x_k}$?  In short, no, but in many cases of interest, sort-of!..

...You can't sample the likelihood!  You can only sample a posterior
pdf!.. why not?.. Give a sense of the difficulties you get into if you
fail here; like discussion with Sven Kreiss on 2013-02-14...

@@

% *********** BJB
% YES!!!! Although you can sample the likelihood if your samples are in
% data space. :)
